---
title: "Introduce Yourself Online"
subtitle: "A workshop @ rstudio::global(2021)"
author: Dr. Alison Presmanes Hill
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "css/grayscale.css", "css/fonts.css"]
    seal: false 
    lib_dir: libs
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      highlightStyle: solarized-light
      highlightLanguage: ["r", "css", "yaml"]
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(collapse = TRUE,
                      fig.retina = 3)
library(xaringanExtra)
```

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

class: title-slide, center, bottom
background-image: url(img/gopher-hero.svg)
background-position: 50% 20%
background-size: 25%
background-color: #ffffff

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author`

---
class: inverse, center, middle

# Why Hugo?

---
class: center, middle

# Why Hugo?

--

Markdown first

--

Content organization (subfolders!)

--

Layout flexibility

--

Multilingual sites

--

Powerful taxonomies

---
class: activity, center, middle

# `r emo::ji("stopwatch")`

## To configure your new Hugo site!

`r emo::ji("clock")` 10 minutes
